\chapter*{Foreword} \label{chap:foreword}

This document contains the collected scribe notes created by the students of
my course titled "Attacks on Secure Implementations", given in
Ben-Gurion University during Spring 2019. 

The following students contributed to the writing process:
\begin{itemize}
    \item \textbf{\Cref{chap:c1_IntroductionAOI}: Introduction.}	Transcription by Michal Hershkoviz,
    graphics by	Shir Frumerman, editing by Yoni Tsionov.
    \item \textbf{\Cref{chap:c2_TemporalSC1}: Temporal Side-Channels 1.}	Transcription by Sagi Nakash,
    graphics by	Ziv Tomarov, editing by Shaked Delarea.
    \item \textbf{\Cref{chap:TemporalSC2}: Temporal Side-Channels 2.}	Transcription by Itay Rosh,
    graphics by	Noga Agmon, editing by Boris Kazarski.
    \item \textbf{\Cref{chap:c4_PowerEM1}: Low Data Complexity Power/EM 1.}	Transcription by Ronen Haber
    and Rotem Yoeli, graphics by Idan Mosseri, editing by Ben Hasson.
    \item \textbf{\Cref{chap:c5_PowerEM2}: Low Data Complexity Power/EM 2.}	Transcription by Barak Davidovich,
    graphics by	Dan Dvorin, editing by Omri Fichman. Section about Template
    Attacks written by Adnan Jaber.
    \item \textbf{\Cref{chap:c7_cacheattacks}: Cache Attacks (Guest Lecture by Prof. Clémentine Maurice).}	Transcription by Ben Amos,
    graphics by	Arbel Levy, editing by Yaniv Agman.
    \item \textbf{\Cref{chap:HighDataComplexityPowerEM1}: High Data Complexity Power/EM 1.}	Transcription by Vitaly
    Dyadyuk, graphics by	Alon Freund, editing by Omer Nizri.
    \item \textbf{\Cref{chap:c8_cpa}: High Data Complexity Power/EM 2.}	Transcription by Rom Ogen,
    graphics by	Shai Cohen and Tomer Gluck, editing by Adi Farshteindiker.
    \item \textbf{\Cref{chap:c9_fault}: Fault Attacks.}	Transcription by Dan Arad,
    graphics by	Dorel Yaffe, editing by Iliya Fayans.
    \item \textbf{\Cref{chap:ethics}: Ethics and Responsible Disclosure.}	Transcription by Ron Korine,
    graphics by	Daniel Portnoy, editing by Roy Radian.
\end{itemize}

The text for chapters 1 to 5 is based on lecture notes in Hebrew originally
created by Yael Mathov. Tom Mahler was responsible for creating the chapter
templates and masterminding the entire editing process. I am grateful to them
and to everybody who contributed to this document.